TCP Congestion Algorithms In Datacenters \\ \vspace{0.3cm} {\large LS Project}

### 2017-12-20 paper/paper.tex
Discussion and future work WIP

@@

\subsubsection{Detection of unaccepted TCP congestion control algorithms}
In \cite{tcp-congestion-identification} a method to remotely identify used TCP congestion avoidance algorithms is described. The paper states that 
they were able to identify all default TCP algorithms, but some non-default algorithms could not be identified. The tests performed are limited to remote web servers, so it requires more research to reliably implement such a method. If this method is deemed reliable, it can be useful to detect whether an unaccepted TCP congestion control algorithm is used as it will not match any of the default TCP algorithms used. Based on that the traffic of the unacceptable TCP congestion control algorithms can be shaped by lowering their priority.

\section{Discussion}\label{sec:discussion}
The CTCP measurements were done on a Windows 10 machine. All other measurements were done on machines running Ubuntu 17.04. This might have introduced issues while measuring the CTCP algorithm versus any other congestion algorithm. CTCP did not show the expected behavior when running the tests. According to our measurements, all other algorithms are fair in sharing bandwidth with other algorithms. However, all measurements from CTCP show different results. We think this might be caused by the way Python sockets or Python calls are handled in Windows 10. We have performed the 0\% loss 0ms delay test on different hardware, which resulted in the same low value of bandwidth usage. When we used \texttt{iperf}, it reached the half of 1 Gbps versus other congestion algorithms as expected. We also increased the amount of bytes sent each time, where it reached 1 Gbps on its own. However, when testing it against another congestion algorithm it still showed the same behavior: performing with a low throughput. Therefore, we think the call handling of Python in Windows encounters more delay than Linux, but this requires more testing.

\section{Future work}\label{sec:futurework}
Running a mixed environment of Linux and Windows where Python is running introduces issues. We expect the call handling of Python in Windows encounters more delay than in Linux, but this requires more testing. The tests for CTCP might have to be performed again when full speeds can be reached by using the same settings. 
The CTCP tests are currently executed on Windows 10. This might also be performed on a Windows Server instance as it possibly handles the network in a different way.

All tests described in this paper can be performed with more parallel connections, so that even when using a lot of parallel connections with two different congestion control algorithms, it is proven that the congestion control algorithms are fair.

@@

\section{Conclusion}\label{sec:conclusion}
Our main research question is: {\it How can a datacenter provide a reliable and performant environment for customers when multiple TCP congestion control algorithms are used in the network?}

>>>>

Because of the exceptional results for CTCP, we performed the test again on
different hardware. This yielded the same result. To verify that it is CTCP and
not our software that performs differently on Windows, we setup a small
experiment using \texttt{iperf}. The setup was the same as our original
experimental setup with one sender on two hosts and two receivers on one host,
only we manually started \texttt{iperf} bandwidth tests rather than doing it in
an automated fashion with Python. In this instance, Windows performed normally
and did not back off exceptionally when introducing another contender.

@@

\subsubsection{Detection of unaccepted TCP congestion control algorithms}

In \cite{tcp-congestion-identification} a method to remotely identify used TCP congestion avoidance algorithms is described. The paper states that 
they were able to identify all default TCP algorithms, but some non-default algorithms could not be identified. The tests performed are limited to remote web servers, so it requires more research to reliably implement such a method. If this method is deemed reliable, it can be useful to detect whether an unaccepted TCP congestion control algorithm is used as it will not match any of the default TCP algorithms used. Based on that the traffic of the unacceptable TCP congestion control algorithms can be shaped by lowering their priority.

\section{Discussion}\label{sec:discussion}

The CTCP measurements were done on a Windows 10 machine because there is no
up-to-date implementation of CTCP for Linux. All other measurements were done
on machines running Ubuntu 17.04. This might have introduced issues while
measuring the CTCP algorithm versus any other congestion algorithm. According
to our measurements, all other algorithms are fair in sharing bandwidth with
each other; only CTCP consistently and excessively reduced its bandwidth
allocation.

Without any concurrent flows, Windows does reach gigabit speed. On different
hardware, it showed the same, recessive behaviour. We think this might be
caused by the way Python socket operations are handled in Windows. When
repeating the test with \texttt{iperf}, which is written in C, this behaviour
no longer occurs. Even when using the Python equivalent of
\texttt{while(true)\{ socket.send(data); \}}, the bandwidth allocation did not
change. We theorize that the difference is caused by something in the
\texttt{send} call. An alternative theory is that Microsoft Windows for
workstations have a different implementation than Microsoft Windows Server
systems.

BBR is the best-performing algorithm in our set, because it barely responds to
packet loss. As mentioned in the results, we see no hard evidence that this
causes other algorithms to reduce their speed further, but there are slight
indications. For example in the test of DCTCP versus BBR, DCTCP reaches around
0.2 to 0.6 megabytes per second. In the test of DCTCP versus BIC, this is 0.3
to 0.7 megabytes per second. The difference is large nor statistically
significant, but it warrants looking into. On the scale of 0.7 megabytes per
second, a tenth of a megabyte does make a difference.

\section{Future work}\label{sec:futurework}

Running a mixed environment of Linux and Windows where Python is running
introduced issues. We expect the send call of Python in Windows is implemented
differently than in Linux, but this requires more testing. The tests for CTCP
should be performed again when the reason for the discrepancy is known and can
be mitigated. The results should also be verified using a Microsoft Windows
Server instance.

Our tests were done using three nodes in a switched network. To make sure our
results hold in practice, future work could introduce a routed network with
many more nodes.

TODO Luc monitoring solution read up

@@

TODO bbr turn on halfway through a test, does others' speed lessen?

\section{Conclusion}\label{sec:conclusion}

Our main research question is: {\it How can a datacenter provide a reliable and performant environment for customers when multiple TCP congestion control algorithms are used in the network?}
